% vim: textwidth=75 rnu ts=2 sw=2 et

% superscriptaddress - don't group by affiliation
% nofootinbib - footnote doesn't go in bibliography
% endfloats - put floats together at the end
% endfloats* - every float will be on its own page
\documentclass[superscriptaddress,nofootinbib,twocolumn]{revtex4-1}

\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{hyperref}              % revtex will link biblio
\usepackage{cleveref}  % Better figures/equations references
                                   % hyperref must come before cleveref

\usepackage{color}      			     % Colored text
\usepackage{soul}                  % Hyphenation, strikethrough
\usepackage{graphicx}              % Figures
\usepackage{siunitx}				       % SI Units

\hyphenation{MSMBuilder}

\begin{document}
\title{MSMBuilder: Statistical Models for Biomolecular Dynamics}
\date{\today}

\author{Matthew P. Harrigan}
\affiliation{Department of Chemistry, Stanford University, Stanford, CA 94305}

\author{Mohammad M. Sultan}
\affiliation{Department of Chemistry, Stanford University, Stanford, CA 94305}

\author{Carlos X. Hern\'andez}
\affiliation{Program in Biophysics, Stanford University, Stanford, CA 94305}

\author{Brooke E. Husic}
\affiliation{Department of Chemistry, Stanford University, Stanford, CA 94305}

\author{Peter Eastman}
\affiliation{Department of Chemistry, Stanford University, Stanford, CA 94305}

\author{Christian R. Schwantes}
\affiliation{Department of Chemistry, Stanford University, Stanford, CA 94305}

\author{Kyle A. Beauchamp}
\altaffiliation[Current address: ]{Counsyl, 180 Kimball Way, South San Francisco, CA 94080}
\affiliation{Memorial Sloan Kettering Cancer Center, New York, NY 10065}

\author{Robert T. McGibbon}
\email[Co-corresponding author: ]{Robert.McGibbon@DEShawResearch.com}
\altaffiliation[Current address: ]{D. E. Shaw Research, 120 W. 45th St., 34th Fl. New York, NY 10036}
\affiliation{Department of Chemistry, Stanford University, Stanford, CA 94305}

\author{Vijay S. Pande}
\email[Co-corresponding author: ]{pande@stanford.edu}
\affiliation{Department of Chemistry, Stanford University, Stanford, CA 94305}
\affiliation{Department of Computer Science, Stanford University, Stanford, CA 94305}
\affiliation{Department of Structural Biology, Stanford University, Stanford, CA 94305}
\affiliation{Program in Biophysics, Stanford University, Stanford, CA 94305}


\begin{abstract}

MSMBuilder is a software package for building statistical models of
high-dimensional time-series data. It is designed with a particular focus
on the analysis of atomistic simulations of biomolecular dynamics such as
protein folding and conformational change.  MSMBuilder is named for its
ability to construct Markov State Models (MSMs), a class of models that has
gained favor among computational biophysicists. In addition to 
both well-established and newer MSM methods,
the package includes complementary
algorithms for understanding time-series data such as hidden Markov models
(HMMs) and time-structure based independent component analysis (tICA).
MSMBuilder boasts an easy to use command-line interface, as well as clear
and consistent abstractions through its Python API (application programming
interface).  MSMBuilder is developed with careful consideration for
compatibility with the broader machine-learning community by following the
design of \texttt{scikit-learn}.  The package is used primarily by
practitioners of molecular dynamics but is just as applicable to other
computational or experimental time-series measurements.
\url{http://msmbuilder.org}

\end{abstract}

\maketitle


\section{Introduction}
\label{sec:intro}
\input{0-intro/intro.tex}

\section{Instructive Examples}
\subsection{Constructing an MSM}
\label{sec:example-src}
\input{1-src/src.tex}

\subsection{Selecting Hyperparameters}
\label{sec:example-gmrq}
\input{2-gmrq/gmrq.tex}

\section{Conclusions}
\label{sec:conclusion}
\input{3-conclusion/conclusion.tex}

\section{Availibility}

MSMBuilder documentation and installation is available at
\url{http://msmbuilder.org}. The source code is available under the
open-source LGPL2.1 license and is accessible at
\url{http://github.com/msmbuilder/msmbuilder}.
The current release at time of writing is version 3.5 \cite{2016-msmbuilder3.5-zenodo}. 
Complete examples can be
found as IPython notebooks in the supporting information and at
\url{http://github.com/msmbuilder/paper}.

\section{Author Contributions}

MPH, MMS, CXH, and BEH wrote the paper.
MPH, MMS, CXH, BEH, PE, CRS, KAB, RTM, and VSP edited the paper.
MPH, MMS, CXH, BEH, PE, CRS, KAB, and RTM wrote the software.
VSP supervised the project.

\section{Acknowledgments}

We extend thanks to all our contributors including
Stephen Liu, Patrick Riley, Steven Kearnes, Joshua Adelman, and Gert Kiss.
We acknowledge funding from NIH grants U19 AI109662 and 2R01GM062868.
MMS acknowledges support from NSF-MCB-0954714.
CXH acknowledges support from NSF GRFP (DGE-114747).
KAB acknowledges support from NIH grant P30CA008747, the Sloan Kettering
Institute, and Starr Foundation grant I8-A8-058.
We acknowledge members of the Chodera, Pande, and No\"{e} labs for helpful
discussions. We thank Ariana Peck for invaluable feedback on this manuscript.

\section{Disclosure}
KAB is currently an employee of Counsyl, Inc.
RTM is currently an employee of D.E. Shaw Research, LLC.
VSP is a consultant of Schrodinger, LLC and a member of its scientific
  advisory board.

\bibliography{msmbuilder.bib,msm.bib,tools.bib}


\end{document}
