Molecular dynamics (MD) is a powerful probe into atomistic dynamics. Recent
advances in technology (specialized hardware \cite{2008-anton} or commodity
GPUs \cite{2009-friedrichs-gpu}) and strategies (massively distributed
architectures \cite{2000-fah, 2010-gpugrid, 2014-kohlhoff-exacycle}) enable
simulations to reach larger size and longer timescales. Increasing
quantities of raw data require novel and sophisticated analysis techniques
\cite{2014-msm-perspective}. Markov state models (MSMs) have gained favor
for drawing interpretable conclusions from time-series data
\cite{2010-everything-msm-afraid-ask, 2014-msm-perspective,
2014-chodera-msm, 2014-msm-book}. Briefly, MSMs model dynamic systems using
a set of discrete states and pairwise transition rates. From these models,
the researcher can compute observables of interest and make predictions.
These models boast a basis in physics, statistical rigor, and ease of
interpretation. Furthermore, MSMs are able to stich together many
independent simulation runs, allowing researchers to fully exploit
distributed computing.

The idea of describing a system by its states and rates is natural for
chemists and biologists, but the estimation of states and rates from finite
data (perhaps molecular dynamics) is not obvious. From the introduction of
MSMs to the biophysics community, algorithmic improvements for constructing
MSMs and computing observables have been the focus of intense study. The
practical implementation of these algorithms has spawned several historical
packages for MSM construction \cite{2009-msmbuilder1, 2011-msmbuilder2,
2012-jemma}. Each of these packages was tied strongly to the best
practices in MSM construction of the time. Due to the fast-moving research
around MSMs, software re-writes were common \cite{2015-pyemma, 2016-htmd}.

We introduce MSMBuilder~3, a community-driven, open source software package
for constructing MSMs. MSMBuilder offers a curated selection of MSM
construction algorithms based on modern advances in the field. MSMBuilder
is implemented in the Python programming language with performance-critical
components written in C. It exposes an extensible API modeled after that of
\texttt{scikit-learn}. The modular design ensures MSMBuilder~3 is adaptable
to future improvements in MSM construction. The package can be invoked
directly from Python or via the command line.

Through two instructive examples, we showcase the capabilities and benefits
of MSMBuilder. In the first, we use MSMBuilder to analyze a biological
system of interest from a dataset composed of more than 20,000
trajectories. This example builds a single MSM using new or refined methods
unavailable in previous versions of the software. The rapid advances in
MSM methods can lead to a ``paradox of choice" for the researcher. In the
second example, we resolve this paradox using MSMBuilder's implementation of novel scoring
functionals for selecting the best models and algorithms in a systematic
way.

% vim: tw=75
