MSMBuilder~3 is a powerful and accessible software package for drawing
interpretable conclusions from time-series data. We used two examples to
demonstrate how MSMBuilder can make sense of a molecular dynamics dataset
consisting of thousands of trajectories in a highly automated and
statistically robust way. In the first example, we construct a ``vanilla''
MSM and show how MSMBuilder enables the construction of
interpretable models that expose the connection between biological function
and structural dynamics.  We highlight the breadth of relevant algorithmic choices for
featurization, normalization, dimensionality reduction, clustering, and MSM
modelling.  In the second instructive example, we acknowledge that the
explosion of choices in parameters and protocol can be overwhelming. We use
the GMRQ score and off-the-shelf cross-validation machinery to do a simple
grid search over tunable parameters to evaluate the relative merit of many
MSMs built on the same MD dataset of a small protein. Since
cross-validation is not a technique unique to biophysics, we leverage the
greater Python machine learning ecosystem for this example.

More broadly, MSMBuilder's power and clarity is derived from its integration
with the machine learning community at large. Our power to focus on
developing methods bespoke to biophysics and time-series analysis comes
from exploiting general-purpose algorithms implemented by respective
experts. The clarity of MSMBuilder's API is due in large part to the
massive amount of effort and skill put into the design of
\texttt{scikit-learn}'s API. As distributed computing and Markov modelling
continue to become more prominent, MSMBuilder offers a sustainable,
extensible, powerful, and easy-to-use set of Python and command-line tools
to help researchers draw meaningful conclusions from their data.

% vim: ts=2 sw=2 et tw=75
